---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)

library(formatR)
library(knitr)
library(janitor)
library(tidyr)
library(zoo)
library(lubridate)
library(hms)
library(dplyr)
library(ggplot2)
library(gtable)
library(grid)
library(ggpubr)
library(kableExtra)
library(scales)
library(hms)
library(stringr)
library(data.table)
library(stringr)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
```

# FY19 Cappex Performance and Comparison to Previous Years 


# Description

`r newthought('In FY19, the Office of Marketing and Brand Management')` at USM contracted with Cappex for one year to acquire HS student inquiries, as it has done for the past several years. 


#

## Contract Details


```{r eval=FALSE, include=FALSE}
# Historical referral quantities per Cappex
# 
# 11/6/2014-11/5/2015: 5124 (1201)
# 
# 11/6/2015-11/5/2016: 4903 (1329)
# 
# 11/6/2016-11/5/2017: 1305
# 
# 11/6/2017-11/5/2018: 1555 
# 
# 11/6/2018 - 11/5/19: 1345

```


* Run time November 6, 2018 - November 5, 2019


* Contract cost = $16,500.00

# Qualifying Criteria: 

+ Sophomores, Juniors, Seniors

+ ME, MA, CT, VT, NH, NY, RI

+ Minimum GPA 2.5


# Findings



```{r}
FY <- c("CY15", "CY16", "CY17", "CY18", "CY19")
```

```{r}
Number_Inquiries_NE <- c(1201, 1329, 1305, 1555, 1345)
```



Per Cappex, the assets we have historically purchased are shown below. 

```{r}
YoY <- cbind.data.frame(FY, Number_Inquiries_NE) %>% rename(Inquiries = Number_Inquiries_NE) %>% mutate(Inquiries = prettyNum(Inquiries, big.mark = ","))
YoY <- YoY %>% 
  rename(Contract_Yr = FY)
kable(YoY)

```


```{r}
Data <- read.csv("C:/Users/christine.iyer/Box/FY19_Inquiries/Cappex Summary/CappexInit11-12-19.csv", header = T, stringsAsFactors = F)

Data <- Data %>% 
  rename(Contract_Yr = Created.Date..group.,
         Anticipated_Start = Anticipated.Start.Term.Year..group.)

```

#

#

#

#


# Enrollment Funnel per our Database by Contract Year 

Unless otherwise stated, Cappex is the **Initial Referral Source**


```{r}

kable(Data %>% group_by(Contract_Yr) %>% 
        filter(Contract_Yr != "Contract 16" & Contract_Yr != "Contract 20") %>% 
        summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled))) 
```

# Enrollment Funnel per our Database by Anticipated Start Year



```{r}

season <- c("Fall 2017 ", "Fall 2018", "Fall 2019 ", "Fall 2020 ", "Fall 2021")

kable(Data %>%
  filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) ) 

```


#

# Enrollment Funnel per our Database by Contract Year and Anticipated Start Year




**Contract Year 2017: 11/6/2016-11/5/2017**

```{r message=FALSE, warning=FALSE}


Data17 <- Data %>% 
        filter(Contract_Yr == "Contract 17") %>% 
        group_by(Contract_Yr, Anticipated_Start) %>% 
        summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
        mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%")) %>% 
        filter(Inquiries > 43) %>%
        mutate(Class = ifelse(Inquiries == 106, "Seniors", 
                              ifelse(Inquiries == 510, "Juniors", 
                                     ifelse(Inquiries == 257, "Sophomores", "Freshmen")))) 
kable(Data17 %>% 
        select(Class, Inquiries, Apps, Admits, Deposits, Enrolls, App_Yield))
```

#

**Contract Year 2018: 11/6/2017-11/5/2018**



```{r message=FALSE, warning=FALSE}

#head(Data)
Data18 <- Data %>% 
        filter(Contract_Yr == "Contract 18") %>% 
        group_by(Contract_Yr, Anticipated_Start) %>% 
        summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
        mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%")) %>% 
        filter(Inquiries > 48) %>%
        mutate(Class = ifelse(Inquiries == 229, "Seniors", 
                              ifelse(Inquiries == 417, "Juniors", 
                                     ifelse(Inquiries == 311, "Sophomores", "Freshmen"))))

kable(Data18 %>% 
        select(Class, Inquiries, Apps, Admits, Deposits, Enrolls, App_Yield))


      
```

#

#

#

**Contract Year 2019: 11/6/2018-11/5/2019**


```{r message=FALSE, warning=FALSE}
Data19 <- Data %>% 
        filter(Contract_Yr == "Contract 19") %>% 
        group_by(Contract_Yr, Anticipated_Start) %>% 
        summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
        mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))%>% 
        filter(Inquiries > 45) %>%
        mutate(Class = ifelse(Inquiries == 98, "Seniors", 
                              ifelse(Inquiries == 917, "Juniors", 
                                     ifelse(Inquiries == 264, "Sophomores", "Freshmen"))))

kable(Data19 %>% 
        select(Class, Inquiries, Apps, Admits, Deposits, Enrolls, App_Yield))
```

# Enrollment Funnel per our Database by State

**Maine**


```{r}
kable(Data %>%
  #filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start, Region) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
    filter(Region == "Maine", Anticipated_Start != "Unsure", Inquiries >= 72) %>% 
    select(Anticipated_Start, Inquiries, Apps, Admits, Deposits, Enrolls) %>% 
    mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))) 

```



#

**Connecticut**

```{r}
kable(Data %>%
  #filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start, Region) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
    filter(Region == "Connecticut", Anticipated_Start != "Unsure", Inquiries>23) %>% 
    select(Anticipated_Start, Inquiries, Apps, Admits, Deposits, Enrolls) %>% 
    mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))) 

```


#

**Massachusetts**


```{r}
kable(Data %>%
  #filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start, Region) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
    filter(Region == "Massachusetts", Anticipated_Start != "Unsure", Inquiries>145) %>% 
    select(Anticipated_Start, Inquiries, Apps, Admits, Deposits, Enrolls) %>% 
    mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))) 

```

#

**New Hampshire**

```{r}
kable(Data %>%
  #filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start, Region) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
    filter(Region == "New Hampshire", Anticipated_Start != "Unsure", Inquiries >22) %>% 
    select(Anticipated_Start, Inquiries, Apps, Admits, Deposits, Enrolls) %>% 
    mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))) 

```

#

**New York**

```{r}
kable(Data %>%
  #filter(Anticipated_Start %in% season) %>% 
  group_by(Anticipated_Start, Region) %>% 
  summarise(Inquiries = sum(Inquiry), 
            Apps = sum(ApplieComplete.App)+ sum(Incomplete.App), 
            Admits = sum(Admitted),
            Deposits = sum(Confirmed),
            Enrolls= sum(Enrolled)) %>% 
    filter(Region == "New York", Anticipated_Start != "Unsure", Inquiries >45) %>% 
    select(Anticipated_Start, Inquiries, Apps, Admits, Deposits, Enrolls) %>% 
    mutate(App_Yield = paste0(round(Apps/Inquiries * 100, 2), "%"))) 

```

#

# Conclusions

* In the preliminary report, we became concerned because we saw a big 67% drop in Cappex inquiries. We decided to address this directly with Aaron Deets, our Cappex Representative. 

* After 2 meetings with him, I requested the list of inquires for the past contract year. The list corroborated over 1,300 inquiries, slightly lower than the number of inquiries they provided the previous yea.  

* I did a quick check and noticed many of the inquiry contact information was not in our database. 

* I addressed this with John Derouche who ultimately diagnosed and remedied the upload problem. 

* Moving forward, I will be included in the weekly email inquiry lists, Cappex and Hobson, to verify upload success.

* I have reconciled the FY19 Cappex inquiry list with our records and the results are shown here. 

* High School Juniors and Sophomores have highest application yields. We did see a very high application yield for Freshmen for the 2017 contract, however the sample size is small and I therefore advise caution.


* We are seeing a growth in applications from students in MA and CT when looking at the data by anticipated start year. 






```{r}
Aaron <- read.csv("C:/Users/christine.iyer/Downloads/Southern Maine Cappex Inquiries 18-19 Contract.csv", header = T, stringsAsFactors = F)
Aaron <- Aaron %>% rename(Email = Email.Address)

```

```{r}
SFMatch <- read.csv("C:/Users/christine.iyer/Downloads/report1573827737406.csv", header = T, stringsAsFactors = F)

```


```{r}
# bew <- merge.data.frame(Aaron,SFMatch, by = "Email")
# dim(bew)
# CappexFinal <- bew %>% group_by(Primary.State.Province,Student.Stage, App.Application.Status, Anticipated.Start.Term.Year, Initial.Referral.Source) %>% summarise(n = n())
# dim(CappexFinal)
# write.csv(CappexFinal, "C:/Users/christine.iyer/Box/FY19_Inquiries/Cappex Summary/CorrectedCappex.csv", row.names = F)

#CorrectCappexTidy <- read.csv("C:/Users/christine.iyer/Box/FY19_Inquiries/Cappex Summary/CorrectedCappexTidied.csv", header = T, stringsAsFactors = F)

```
```{r}
# sum(CorrectCappexTidy$Inquiry)
# kable(CorrectCappexTidy %>% group_by(Antic.Start) %>% summarise(Inquiry = sum(Inquiry), Applicant = sum(Applicant), Enrolled = sum(Enrolled)))
# kable(CorrectCappexTidy %>% group_by(Initial.Referral) %>% summarise(Inquiry = sum(Inquiry), Applicant = sum(Applicant), Enrolled = sum(Enrolled)) %>%  arrange(desc(Enrolled)))
```

#


* Duplicates in our system may cause our numbers to vary from others used.

* Year over year, does revenue justifies the contract cost? **Yes** 

* Has Cappex  decreased from FY18 to FY19 as a 1st referral source. **No** 

* After showing growth from FY16 to FY18, "All Referrals" showed no change from FY18 to FY19.**The vast majority of Contract Yr 19 inquiries were Juniors and Sophomores. I would anticipate if we continue to see grouth it will be among HS students who have anticipated start years of Fall 2020 and later.**

* Does one class convert at a higher rate than another? **Juniors and Sophomores convert from inquiries to applicants at higher rates than seniors.**

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
